My title

### 2022-02-21 outputs/paper/paper.Rmd
Replicated Figure 2e in the original paper

```{r Figure2b, fig.cap="*Note*: Birth rates by race and ethnicity are gathered from CDC Vital Statistics Births Reports. The Data Appendix provides detailed information on the specific data source.", echo=FALSE, warning=FALSE, message=FALSE}
df_2b %>%
  ggplot(aes(x = year, y = value)) + 
  geom_line(aes(color = variable)) +
  geom_vline(xintercept = 2007, linetype="dashed") +
  geom_text(aes(x = 2007, label="2007", y = 130), nudge_x = 2.3, nudge_y = 1.5) + labs(title = "b: Race and ethnicity") +
  scale_color_discrete(name = "Race and Ethnicity Groups",
                       limits = c("brate_whitenh", "brate_blacknh", "brate_hisp"),
                       labels = c("White, non-Hispanic", "Black, non-Hispanic", "Hispanic")) +
  scale_x_continuous(name = NULL, breaks = c(1990, 1995, 2000, 2005, 2010, 2015, 2020)) +
  scale_y_continuous(name = "Births per 1,000 women in different race groups", breaks = c(0, 20, 40, 60, 80, 100, 120, 140), limits = c(0, 140)) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())
```

>>>>

```{r Figure2b, fig.cap="*Note*: Birth rates by race and ethnicity are gathered from CDC Vital Statistics Births Reports. The Data Appendix provides detailed information on the specific data source.", echo=FALSE, warning=FALSE, message=FALSE}
df_2b %>%
  ggplot(aes(x = year, y = value)) + 
  geom_line(aes(color = variable)) +
  geom_vline(xintercept = 2007, linetype="dashed") +
  geom_text(aes(x = 2007, label="2007", y = 130), nudge_x = 2.3, nudge_y = 1.5) + labs(title = "b: Race and ethnicity (ages 15 - 44)") +
  scale_color_discrete(name = "Race and Ethnicity Groups",
                       limits = c("brate_whitenh", "brate_blacknh", "brate_hisp"),
                       labels = c("White, non-Hispanic", "Black, non-Hispanic", "Hispanic")) +
  scale_x_continuous(name = NULL, breaks = c(1990, 1995, 2000, 2005, 2010, 2015, 2020)) +
  scale_y_continuous(name = "Births per 1,000 women in different race groups", breaks = c(0, 20, 40, 60, 80, 100, 120, 140), limits = c(0, 140)) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Replicate Figure 2e
fig_2e_data <- read_csv("~/US_birth_rates_folder/inputs/data/fig_2e_data.csv")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
df_2e <- fig_2e_data %>%
  gather(key = "variable", value = "value", -year) %>%
  drop_na()
```

```{r Figure2e, fig.cap="*Note*: Birth rates by marital status are gathered from CDC Vital Statistics Births Reports. The Data Appendix provides detailed information on the specific data source.", echo=FALSE, warning=FALSE, message=FALSE}
df_2e %>%
  ggplot(aes(x = year, y = value)) + 
  geom_line(aes(color = variable)) +
  geom_vline(xintercept = 2007, linetype="dashed") +
  geom_text(aes(x = 2007, label="2007", y = 130), nudge_x = 2.3, nudge_y = 1.5) + labs(title = "e: Marital status (ages 15 - 44)") +
  scale_color_discrete(name = "Marital Status",
                       limits = c("brate_unmarried", "brate_married"),
                       labels = c("Unmarried", "Married")) +
  scale_x_continuous(name = NULL, breaks = c(1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020)) +
  scale_y_continuous(name = "Births per 1,000 women for different marital status", breaks = c(0, 20, 40, 60, 80, 100, 120, 140), limits = c(0, 140)) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())
```
